Approximation as Differentiation

### 2025-05-24 main/formal-structures.tex
interpreted -> regarded.

\noindent Galois connections thus generalise order isomorphisms. The $\adj$ notation is justified because a
Galois connection $f \adj g: X \to Y$ can also be seen an adjunction between poset categories, with monotone
$f$ and $g$ interpreted as functors; $f$ is usually referred to as the \emph{upper} (right) adjoint and $g$ as
the \emph{lower} (left) adjoint. Galois connections compose component-wise, with $\id_X \adj \id_X: X \to X$
as the unit for composition, and thus form a category $\PosGal$ with all posets as objects and all Galois
connections between them as morphisms.

>>>>

\noindent Galois connections thus generalise order isomorphisms. The $\adj$ notation is justified because a
Galois connection $f \adj g: X \to Y$ can also be seen an adjunction between poset categories, with monotone
$f$ and $g$ regarded as functors; $f$ is usually referred to as the \emph{upper} (right) adjoint and $g$ as
the \emph{lower} (left) adjoint. Galois connections compose component-wise, with $\id_X \adj \id_X: X \to X$
as the unit for composition, and thus form a category $\PosGal$ with all posets as objects and all Galois
connections between them as morphisms.

### 2025-05-24 main/framework.tex
ACM requires title case for subsection headings.
interpreted -> regarded.

\subsection{Grothendieck construction for indexed categories}
\label{sec:Grothendieck}

@@

\begin{definition}[Category of $X$-indexed families]
For any set $X$ (interpreted as a discrete category) and any category $\cat{C}$, recall that the functor
category $\Func{X}{\cat{C}}$ has as objects all functors $F: X \to \cat{C}$, namely $X$-indexed families of
objects of $\cat{C}$, and as morphisms from $F \to G$, all families of morphisms $\eta(x): F(x) \to G(x)$ in
$\cat{C}$ for every $x \in X$, with naturality trivial because $X$ has only identity morphisms.
\end{definition}

@@

\subsection{Category of families}
\label{sec:Fam}

@@

\subsection{\GPS via the Grothendieck construction}

@@

\subsection{Interpreting higher-order programs}

>>>>

\subsection{Grothendieck Construction for Indexed Categories}
\label{sec:Grothendieck}

@@

\begin{definition}[Category of $X$-indexed families]
For any set $X$ (regarded as a discrete category) and any category $\cat{C}$, recall that the functor
category $\Func{X}{\cat{C}}$ has as objects all functors $F: X \to \cat{C}$, namely $X$-indexed families of
objects of $\cat{C}$, and as morphisms from $F \to G$, all families of morphisms $\eta(x): F(x) \to G(x)$ in
$\cat{C}$ for every $x \in X$, with naturality trivial because $X$ has only identity morphisms.
\end{definition}

@@

\subsection{Category of Families}
\label{sec:Fam}

@@

\subsection{Galois Slicing via the Grothendieck Construction}

@@

\subsection{Interpreting Higher-Order Programs}
